abxD01 Paper

### 2015-03-06 PAPER.Rmd
Update sections to supfig2

cor<-signif(results[1,1],2)
legend("topright", inset=0.05, legend=legend.labels.top, pch=pch.top, col=colors.top,  pt.cex=1.5, cex=1, bty="n", y.intersp=1.5)

@@

> ### Differences between recovery days' thetayc
> 
> ### Statistical comparison of delayed and on time CFU results

>>>>

legend("topright", inset=0.05, legend=legend.labels.top, pch=pch.top, col=colors.top,  pt.cex=1.5, cex=1, bty="n", y.intersp=1.5)

@@

![**Supplemental Figure 2.**](supplemental/sfigure2.png)

**Supplemental Figure 2. Structural distances between untreated and recovery days.** This figure shows the average theta YC distance between pretreatment and recovery days by antibiotic group. Day -11 represent untreated mice. Day 0 represents day of *C. difficile* challenge. Error bars show standard error of the mean.

> ### Differences between recovery days' thetayc

```{r, eval=FALSE}
file = "~/Desktop/mothur/abxD01/abxD01.final.an.unique_list.0.03.recovery.vancomycin.thetayc.0.03.lt.ave.dist"
diffs <- getDistDiffs(file=file)

metadata <- read.delim(file="~/Desktop/mothur/abxD01/searchme.txt", header = T, stringsAsFactors=F)
metadata$sample[1951] <- "007-1D1" # ID was messed up
names(metadata)[3] <- "group"

plot.dist.from(dist.from = diffs)

> ### Statistical comparison of delayed and on time CFU results
